Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-17 paper/aldebaran.tex
accents

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coude
échelle spectrograph of the Thüringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
Échelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}

>>>>

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coud\'{e}
\'{e}chelle spectrograph of the Th\"{u}ringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
\'{E}chelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}
